Updates on the Exoplanet Orbit Database

### 2014-02-25 draft/ms.tex
Add paragraph to introduction.

Since the first peer-reviewed list of exoplanets with robust orbits
\citep{Butler2002,Butler2006}, the count of exoplanets has increased
from less than 200 to over 1000 today (exoplanets.org). Before the
launch of NASA's \kepler\ mission \citep{Borucki2010}, most confirmed
exoplanets were discovered via the precise radial velocity (RV)
method. However, since 2009, \kepler\ has contributed over $\sim$ 400
confirmed exoplanets (ZZZ need citation update once the $>300$
\kepler\ release comes out) as well as over 3000 exoplanet candidates
(\kepler\ Objects of Interest, KOIs; e.g.~\citealt{Batalha2013}).

Recent development of exoplanet discoveries, especially
\kepler\ discoveries.

The business of keeping track of exoplanet discoveries, where EOD
stands, and a brief history of EOD.

>>>>

% Recent development in exoplanet discoveries
Since the first peer-reviewed list of exoplanets with robust orbits
\citep{Butler2002,Butler2006}, the count of exoplanets has increased
from less than 200 to over 1000 as of March 2014
(exoplanets.org). Before the launch of NASA's \kepler\ mission
\citep{Borucki2010}, most confirmed exoplanets were discovered via the
precise radial velocity (RV) method. However, since 2009, \kepler\ has
contributed over $\sim$ 400 confirmed exoplanets (ZZZ need citation
update once the $>300$ \kepler\ release comes out) as well as over
3000 exoplanet candidates (\kepler\ Objects of Interest, KOIs;
e.g.~\citealt{Batalha2013}).

% The business of tracking planet discoveries
As the number of exoplanet discoveries keeps rising, it is important
to keep tracking these discoveries and cataloging the orbital
parameters and host star properties of exoplanet systems. There are
several entities that are devoted to this effort, including the
Exoplanet Orbit Database and Exoplanets Data Explorer\footnote{See
  \url{http://exoplanets.org}.} \citep{Wright2011}, the Extrasolar
Planets Encyclopaedia\footnote{See \url{http://exoplanet.eu}.}
\citep{Schneider2011}, the NASA Exoplanet Archive\footnote{See
  \url{http://exoplanetarchive.ipac.caltech.edu}.}
\citep{Akeson2013}, and so on.

% A brief history of EOD
